Supporting Information : Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-07-13 MainText.Rmd
started writing intro

---
title: "Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology"
author: "Shyamolina Ghosh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

\noindent\makebox[\linewidth]{\rule{\columnwidth}{1pt}}

\scriptsize

\textbf{ABSTRACT:}  \small write abstract here

@@

\noindent\makebox[\linewidth]{\rule{\columnwidth}{1pt}}

\normalsize

@@

<!--Background for extinction risk in ecological model-->

<!--How extinction risk is related to extreme events : past studies-->

@@

<!--our objective ?-->
We explored the potential use of asymmetric tail-dependence in copula 
for understanding the extinction risk of populations towards extreme climatic event in ecology
by addressing the following questions: (Q1) Does nature of tail dependence in vital rates
of a single-patch age-structured population model affect extinction risk of that population differently?
We hypothesized population might have higher extinction risk if vital rates are left-tail dependent.
(Q2) How does asymmetric tail-dependent noises across multiple patches influence extinction 
risk of a nonlinear metapopulation model with density dependence? Our speculation is that the general finding 
from density-independent metapopulation model [BIVAN paper results of Lewinton-Cohen model]
(higher extinction risk if noises across patches were 
left-tail dependent than the one if noises came with right-tail dependence) holds true only in
the under-compensatory regime, but should be reverse if the model shows over-compensatory dynamics. 
(Q3) We further hypothesize that when there is no dispersal, the above-said switching should occur
near the critical parameter value where the deterministic model shows transition from 
under-compensatory to over-compensatory dynamics.

>>>>

---
title: "Extreme climatic events with asymmetric tail-dependence affect population-extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

\noindent \emph{Affiliations:}

\noindent Ghosh: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66045, USA

\noindent Reuman: Department of Ecology and Evolutionary Biology and Kansas Biological Survey, University of Kansas, Lawrence, KS, 66047, USA; Laboratory of Populations, Rockefeller University, 1230 York Ave, New York, NY, 10065, USA

\newpage

\noindent \textbf{ABSTRACT} 
<!--200 words limit : J Am Nat-->

@@

\newpage

@@

<!--how common are the extreme events? 
what are the implication of extreme events on life history? 
any negative or positive effects? : past literatures-->
For past few decades, there have been evidences that anthropogenic climate change 
is causing more frequent extreme events [ref] (e.g. temperature or precipitation extremes,
heat-waves, wild-fire) which show shifts in its mean, 
in the variability of the distribution, as well as changes in its 
symmetry or skewness. Such extreme climatic events (ECE) can pose severe
impacts at the individual, population, community and ecosystem level (e.g. Parmesan,
Root & Willig 2000; van de Pol et al. 2010b; Hoover,
Knapp & Smith 2014). Therefore, understanding the long-term impacts of changes 
in ECEs has been a longstanding interest in ecological research, specically in modelling 
extreme-risks [ref:Risk Analysis, Vol. 32, No. 11, 2012].

<!--How extinction risk is related to extreme events : past studies
consequences of extreme events on population life history, community-->

@@

<!--our objective ?-->
We explored the potential use of asymmetric tail-dependence in copula 
for understanding the extinction risk of populations towards extreme climatic event in ecology
by addressing the following questions: (Q1) Does nature of tail dependence in vital rates
of a single-patch age-structured population model affect extinction risk of that population differently?
We hypothesized population might have higher extinction risk if vital rates are left-tail dependent.
(Q2) How does asymmetric tail-dependent noises across multiple patches influence extinction 
risk of a nonlinear metapopulation model with density dependence? Our speculation is that the general finding 
from density-independent metapopulation model [@Ghosh_copula]
(higher extinction risk if noises across patches were 
left-tail dependent than the one if noises had right-tail dependence) holds true only in
the under-compensatory regime, but should be reverse if the model shows over-compensatory dynamics. 
(Q3) We further hypothesize that when there is no dispersal, the above-said switching should occur
near the critical parameter value where the deterministic model shows transition from 
under-compensatory to over-compensatory dynamics.

### 2019-07-13 SuppMat.Rmd
started writing intro

---
title: "Supporting Information : Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology"
author: "Shyamolina Ghosh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

>>>>

---
title: "Supporting Information : Extreme climatic events with asymmetric tail-dependence affect population-extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"
